%-------------------------
% Resume in Latex
% Author : Ian Ulery
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
  \begin{center}
    \textbf{\Huge \scshape Ian Ulery} \\
    \vspace{3pt}
    \textbf{
      \small{
        Senior Software Engineer $|$ Cloud-Native Application Architect $|$ Technical Leader
      }
    } \\
    \vspace{3pt}
    \small
      Carmel, IN $|$
      xxx-xxx-xxxx $|$
      \href{mailto:x@x.com}{\underline{x@x.com}} $|$
      \href{https://linkedin.com/in/ianulery}{\underline{linkedin.com/in/ianulery}} $|$
      \href{https://github.com/ianulery}{\underline{github.com/ianulery}}
  \end{center}

  \section{Professional Summary}
    \small{
      Results-driven Senior Software Engineer with 10+ years leading full-stack, cloud-native application development across high-impact organizations including NASA's Jet Propulsion Laboratory, AT\&T Interactive, and UCLA. Adept at architecting scalable systems, mentoring junior engineers, and driving Agile DevOps initiatives. Proven expertise in Ruby, Swift/Kotlin for mobile, and modern web technologies across AWS/Azure ecosystems. Experienced in training and deploying AI/ML models, contributing to intelligent system design and automation. Passionate about clean, maintainable code and fostering innovation through technical leadership and collaboration.
    }

  \section{Achievements and Core Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
        \textbf{Awards}{: NASA Team Honor Award, UCLA STAR Award, JPL Bonus Award, National SMART Grant} \\
        \textbf{Languages}{: C++, Python, Java, Ruby, Swift, Objective-C, Kotlin, JavaScript, HTML, CSS, SQL} \\
        \textbf{Cloud \& DevOps}{: Azure (Hybrid Cloud), AWS, Heroku, Docker, CI/CD pipelines} \\
        \textbf{Tools}{: Git, RSpec, Cucumber, NewRelic APM, Agile/Scrum, Jira} \\
        \textbf{Architectures}{: Microservices, RESTful APIs, Containerization} \\
        \textbf{Databases}{: PostgreSQL, MySQL, SQL Server}
      }}
    \end{itemize}

  \section{Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Information Technology Manager}{Sep. 2014 -- Present}
        {BGI}{Ventura, CA (Remote)}
      \resumeItemListStart
        \resumeItem{Lead development of web (Ruby on Rails) and mobile (iOS) line-of-business applications, following 
        agile and test-driven methodologies, with continuous deployment to a containerized production 
        environment.}
        \resumeItem{Meet with stakeholders to define requirements for line-of-business applications that improve operational efficiency.}
        \resumeItem{Provision and administer servers (Linux, Windows) and network in a Microsoft Azure hybrid cloud 
        configuration.}
        \resumeItem{Consulting client converted to W-2 employment in 2014 for retention.}
      \resumeItemListEnd

      \resumeSubheading
        {Vice President, Technology}{Sep. 2014 -- Apr. 2020}
        {Thompson Capital}{Los Angeles, CA}
        \resumeItemListStart
          \resumeItem{Contributed more than \textbf{4,000 commits} in Ruby, Swift, Kotlin, Objective-C, JavaScript, and other supporting languages. }  
          \resumeItem{Served as technical co-founder of a streaming media
          startup initiative.}
          \resumeItem{Lead development of native iOS (Swift, Objective-C) and
          Android (Kotlin) mobile applications, following agile methodologies. }
          \resumeItem{Lead development of a Ruby on Rails web service API, utilizing test-driven development (RSpec, Cucumber) and agile methodologies, with continuous deployment to a cloud environment (Heroku, Amazon AWS).}
          \resumeItem{Utilized NewRelic APM to monitor performance of cloud web service API, ensuring low request processing times, low error rates, and to identify areas of the codebase where performance can be improved.}
          \resumeItem{Implemented and deployed AI model for metadata augmentation utilizing Python, Keras, and TensorFlow.}
          \resumeItem{Represented company in fundraising efforts.}
        \resumeItemListEnd

      \resumeSubheading
        {Programmer Analyst III}{Jun. 2011 -- Sep. 2014}
        {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Received a STAR award for individual contribution based on
        exceptional creativity and technical performance in developing an online
        video streaming platform.}
        \resumeItem{Lead development of a Ruby on Rails web application using
        test-driven development and agile methodologies.}
        \resumeItem{Shared administration of more than 100 Linux and Windows
        servers.}
      \resumeItemListEnd

      \resumeSubheading
        {Software and Computing Systems Undergraduate Student}{Apr. 2009 -- Jun. 2011}
        {NASA Jet Propulsion Laboratory}{Pasadena, CA}
      \resumeItemListStart
        \resumeItem{Received a NASA Team Honor Award for outstanding achievement
        in delivering Engineering Communities of Practice for knowledge sharing
        across NASA as part of the NASA Engineering Network.}
        \resumeItem{Presenter at the 2011 JPL Open House.}
        \resumeItem{Designed and implemented v1 of the NASA/JPL Space Images
        iPad application.}
        \resumeItem{Implemented version 2 update of the NASA/JPL Space Images
        iPhone application, with more than 1 million downloads.}
        \resumeItem{Developed Java J2EE and JSR-168 compliant portlets to extend
        functionality of Vignette Portal.}
        \resumeItem{Developed JSR-168 compliant portlets leveraging the Java
        Spring Portlet MVC framework to extend functionality of Liferay Portal,
        using Eclipse Studio.}
      \resumeItemListEnd

      \resumeSubheading
        {Software Engineer Intern}{Jun. 2008 -- Oct. 2008}
        {AT\&T Interactive}{Glendale, CA}
      \resumeItemListStart
        \resumeItem{Designed and implemented prototype of a location-based mobile search app for iPhone, utilizing a Ruby on Rails web service layer and iPhone geolocation functionality. The released app was selected as a New York Times App of the Week, and was featured by technology blogs including Gizmodo.}
        \resumeItem{Developed internal quality analysis tools and vertical search portals utilizing Ruby on Rails, as part of AT\&T Interactive's Research and Development group.}
      \resumeItemListEnd

      \resumeSubheading
        {Web Application Developer (Work-Study)}{Oct. 2008 -- Jun. 2008}
        {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Developed a web-based employee vacation accrual and leave tracking system utilizing Microsoft ASP.NET (VB), SQL Server, MS Visual Studio, and IIS, saving \textbf{190} administrative work hours each year.}
      \resumeItemListEnd

      \resumeSubheading
      {Associate Web Developer (Intern)}{Aug. 2007 -- Oct. 2007}
      {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Developed an online advertisement delivery web-application to provide targeted ad placement with centralized campaign management for QAD's websites.}
        \resumeItem{Designed and developed an intranet website for information related to the company's flagship product, in collaboration with team members in Antwerp, Belgium and Tokyo, Japan.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

    \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {University of California, Los Angeles}{Los Angeles, CA}
        {Bachelor of Science in Cognitive Science, Specialization in Computing (GPA: 3.24/4.0)}{Jun. 2011}
    \resumeSubHeadingListEnd

    \section{Awards}
    \vspace*{-1.4\multicolsep}
    \begin{multicols}{2}
      \begin{itemize}
        \setlength{\parskip}{0pt}
        \setlength{\itemsep}{0pt plus 1pt}
        \small{
          \item{NASA Team Honor Award}
          \item{UCLA STAR Award}
          \item{JPL Bonus Award}
          \item{National SMART Grant}
          \item{Orfalea Foundation Scholarship}
          \item{Daniel and Anne Hawkes Memorial Scholarship}
          \item{Philip and Frances Carpel Scholarship}
          \item{Santa Barbara Host Lions Club Scholarship}
        }
      \end{itemize}
    \end{multicols}

\end{document}
